Analysis

### 2022-07-02 CTCF_Threshold.Rmd
Figure tweaks

mtx_to_plot <- pivot_longer(gr_summary, cols = c("TP", "FP"), names_to = "Type")
ggplot(mtx_to_plot, aes(x = Threshold, y = value, color = Type)) +
  geom_line() +
  scale_x_continuous(breaks = thresholds, labels = scientific) +
  scale_y_continuous(breaks = seq(0, 1, 0.1))   + 
  scale_color_manual(values = mycols[1:2]) +
  coord_trans(x ="log10") +
  geom_vline(xintercept = 1E-6, linetype = "dashed", color = "black") +
  theme_bw() +
  theme(panel.grid.major = element_blank(), 
      panel.grid.minor = element_blank(), 
      # axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
      plot.title = element_text(hjust = 0.5),
      legend.text = element_text(size = 6)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
  xlab("FIMO p-value threshold") +
  ylab("FP/TP rate")

fileNameOut1 <- file.path(dir_data, "results", "Figure_human_pvalues_threshold.svg")
ggsave(filename = fileNameOut1, width = 4, height = 2)
# dev.off()
# svg(filename = fileNameOut1, width = 7, height = 3)
# print(p)
# dev.off()

>>>>

mtx_to_plot <- pivot_longer(gr_summary, cols = c("TP", "FP"), names_to = "Type")
ggplot(mtx_to_plot, aes(x = Threshold, y = value, color = Type)) +
  geom_line() +
  scale_x_continuous(breaks = thresholds, labels = scientific) +
  scale_y_continuous(breaks = seq(0, 1, 0.2))   + 
  scale_color_manual(values = mycols[1:2]) +
  coord_trans(x ="log10") +
  geom_vline(xintercept = 1E-6, linetype = "dashed", color = "black") +
  theme_bw() +
  theme(panel.grid.major = element_blank(), 
      panel.grid.minor = element_blank(), 
      # axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
      plot.title = element_text(hjust = 0.5),
      legend.text = element_text(size = 6)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
  xlab("FIMO p-value threshold") +
  ylab("FP/TP rate")

fileNameOut1 <- file.path(dir_data, "results", "Figure_human_pvalues_threshold.svg")
ggsave(filename = fileNameOut1, width = 4.5, height = 1.5)
# dev.off()
# svg(filename = fileNameOut1, width = 7, height = 3)
# print(p)
# dev.off()

### 2022-07-02 FIMO_EDA.Rmd
Figure tweaks

ggplot(pvals, aes(x = `-log10(p-value)`, color = MotifDB)) +
  geom_density() +
  geom_vline(xintercept = -log10(pval_threshold), linetype = "dashed", color = "red") +
  scale_color_manual(values = mycols[1:6]) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), 
      panel.grid.minor = element_blank(), 
      # axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
      plot.title = element_text(hjust = 0.5),
      legend.text = element_text(size = 6)) +
      # legend.key.height = unit(0.2, "mm"),
      # legend.key.width = unit(5, "mm")) +
  ylab("Density")

fileNameOut1 <- file.path(dir_data, "Figure_human_pvalues.svg")

dev.off()
svg(filename = fileNameOut1, width = 7, height = 3)
print(p)
dev.off()
```

>>>>

ggplot(pvals, aes(x = `-log10(p-value)`, color = MotifDB)) +
  geom_density() +
  geom_vline(xintercept = -log10(pval_threshold), linetype = "dashed", color = "black") +
  scale_color_manual(values = mycols[1:6]) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), 
      panel.grid.minor = element_blank(), 
      # axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
      plot.title = element_text(hjust = 0.5),
      legend.text = element_text(size = 6)) +
      # legend.key.height = unit(0.2, "mm"),
      # legend.key.width = unit(5, "mm")) +
  ylab("Density")

fileNameOut1 <- file.path(dir_data, "Figure_human_pvalues.svg")
ggsave(filename = fileNameOut1, width = 6.4, height = 1.6)

# dev.off()
# svg(filename = fileNameOut1, width = 7, height = 2)
# print(p)
# dev.off()
